### 2018-01-10 master/paper.tex
Fix file format to unix from dos

>>>>

\section{Performance of TLSF+TECS}

TLSF+TECS provides a functionality that acquires statistical information on dynamic memory usage status.
It is possible to analyze the operation status of TLSF such as GC on RiteVMs because TLSF+TECS acquires memory statistical information: the frequency of memory allocation/deallocation and the usage size of heap area.

Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
    \caption{Memory usage of RiteVM (mruby VM) by TLSFStatistics component}
    \label{fig:EvaluationOfTLSFStatistics}
\end{figure}
